Exploiting the Social Graph: Increasing Engagement via Collaborative Interactive Evolution

### 2017-02-08 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
Format
And eliminate traces of anonymity. Added GitHub repos, but I am not
sure that address is correct. Please @mariosky check and substitute if
needed (but bear in mind the length)

\author{\IEEEauthorblockN{Mario García-Valdez, Amaury Hernández Águila, Alejandra Mancilla}
\IEEEauthorblockA{Instituto Tecnológico de Tijuana\\
Tijuana, Mexico\\
Email: (mario,amherag)@tectijuana.edu.mx,
amherag@tectijuana.edu.mx,alejandra.mancilla@gmail.com}
\and
\IEEEauthorblockN{Juan Julián Merelo Guervós}
\IEEEauthorblockA{Universidad de Granada, CITIC\\
Email: jmerelo@geneura.ugr.es}
}

@@

The link used in the call for participation
was shortened Google URL, that provides metadata and analytics for the
users that click on it. 
In table \ref{tab:urls} the URL for each deployment in the Heroku platform is shown,
along with the short URL and the analytics link. In the same table a link to the GitHub 
application repository used to deploy to Heroku is also listed.    
%Isn't this anonymous? - JJ
% like in double blind? I think so, that is why no link is given in the table. - Mario

\begin{table}
  \small
  \caption{ Deployment data. URLs were {\tt
      evodrawings0(1,2,3).herokuapp.com}. For analytics URLs, add {\tt
    .info}.}
  \label{tab:urls} 
  \centering
  \small
  \begin{tabular}{l l l }
    \hline\noalign{\smallskip}
     Deployment &  Shortened URL &  Github Repository \\
    \noalign{\smallskip}\hline\noalign{\smallskip}
    B   & goo.gl/jLis4Q &   \\ \hline
    G   & goo.gl/jqjNy5 &  \\ \hline
    GG  & goo.gl/J8TCe1 &   \\ \hline
    \end{tabular}
\end{table}

@@

\section*{Acknowledgment}
Space reserved for Acknowledgment text

>>>>

\author{\IEEEauthorblockN{Mario Garc\'ia-Valdez, Amaury Hern\'andez-\'Aguila, Alejandra Mancilla}
\IEEEauthorblockA{Instituto Tecnol\'ogico de Tijuana\\
Tijuana, Mexico\\
Email: (mario,amherag)@tectijuana.edu.mx,alejandra.mancilla@gmail.com}
\and
\IEEEauthorblockN{Juan Juli\'an Merelo Guerv\'os}
\IEEEauthorblockA{Universidad de Granada, CITIC\\
Email: jmerelo@geneura.ugr.es}
}

@@

The link used in the call for participation
was shortened Google URL, that provides metadata and analytics for the
users that click on it. 
In table \ref{tab:urls} the URL for each deployment in the Heroku platform is shown,
along with the short URL and the analytics link. In the same table a link to the GitHub 
application repository used to deploy to Heroku is also listed.

\begin{table}
  \small
  \caption{ Deployment data. URLs were {\tt
      evodrawings0(1,2,3).herokuapp.com}. For analytics URLs, add {\tt
    .info}.}
  \label{tab:urls} 
  \centering
  \small
  \begin{tabular}{l l l }
    \hline\noalign{\smallskip}
     Deployment &  Shortened URL &  Github Repository \\
    \noalign{\smallskip}\hline\noalign{\smallskip}
    B   & goo.gl/jLis4Q &  mariosky/evospace-js \\ \hline
    G   & goo.gl/jqjNy5 &  mariosky/evospace-js\\ \hline
    GG  & goo.gl/J8TCe1 &  mariosky/evospace-js \\ \hline
    \end{tabular}
\end{table}

@@

\section*{Acknowledgment}

This work has been supported in part by: de Ministerio espa\~{n}ol de
Econom\'{\i}a y Competitividad under project TIN2014-56494-C4-3-P
(UGR-EPHEMECH).
